### 2019-07-26 paper/paper.tex
first round of fixes

% JuliaCon proceedings template
\documentclass{juliacon}
\usepackage{amsmath}
\setcounter{page}{1}

\begin{document}
\input{header}
\maketitle
\begin{abstract}

@@

Finally, we have the problem of intercomunication costs. Data-parallelism -generally- involves intense needs of inter-thread-communication. While task-parallelism communication costs depends on Load-Balancing choices (i.e. Dynamic vs Static), they are usually lower than data-parallelism ones \footnote{At least when Static Load Balancing is implemented, because it allows for Coarse-grained granularity. \vskip 6pt

@@

\subsection{OLS estimation}
\label{subsub:ols}
Efficient Ordinary Least Squares (OLS) algorithms rely on Linear Algebra operations (matrix decomposition, matrix inversion, etc.).\footnote{Optimization alternatives (i.e. Gradient descent), while quite inefficient for linear models, can also be used for non-linear estimations. The traditional $(X'X)^{-1}$ operation could be time-expensive with unstable solutions under certain conditions. A preferred method is the QR-decomposition developed by Francis and Kublanovskaya. The QR factorization allows us to decompose any full rank $N \times p$ matrix $\bar{X}$ as:

>>>>

% JuliaCon proceedings template
\documentclass{juliacon}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{amsmath}
\setcounter{page}{1}

\input{header}
\begin{document}
\maketitle
\begin{abstract}

@@

Finally, we have the problem of intercomunication costs. Data-parallelism -generally- involves intense needs of inter-thread-communication. While task-parallelism communication costs depends on Load-Balancing choices (i.e. Dynamic vs Static), they are usually lower than data-parallelism ones \footnote{At least when Static Load Balancing is implemented, because it allows for Coarse-grained granularity}. \vskip 6pt

@@

\subsection{OLS estimation}
\label{subsub:ols}
Efficient Ordinary Least Squares (OLS) algorithms rely on Linear Algebra operations (matrix decomposition, matrix inversion, etc.).\footnote{Optimization alternatives (i.e. Gradient descent), while quite inefficient for linear models, can also be used for non-linear estimations.} The traditional $(X'X)^{-1}$ operation could be time-expensive with unstable solutions under certain conditions. A preferred method is the QR-decomposition developed by Francis and Kublanovskaya. The QR factorization allows us to decompose any full rank $N \times p$ matrix $\bar{X}$ as:
